---
title: "Assignment 7"
author: "Jennifer Horowitz"
date: "10/31/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning= FALSE, message = FALSE) 
```

```{r}
library(tidyverse)
library(sf)
library(leaflet)
library(htmltools)
library(htmlwidgets)
library(raster)
library(gstat)
library(spatial)
```

```{r}
apartmentrentals <- st_read(
  "https://data.cambridgema.gov/api/geospatial/iect-ma2e?method=export&format=KML")
```

## Plotting Cambridge neighborhoods in Leaflet

```{r}
cambridge_nhoods <- st_read("https://data.cambridgema.gov/api/geospatial/4ys2-ebga?method=export&format=GeoJSON", quiet = TRUE) %>%
  dplyr::select(name)

leaflet(cambridge_nhoods) %>%
  addProviderTiles(providers$Stamen.TonerLite) %>%
  addPolygons(highlightOptions = highlightOptions(fillColor = "orange", 
                                                  fillOpacity = 1),
              label = ~name, 
              weight = 1) 
```
## Calculating how many apartment rentals per neighborhood 

```{r}
cambridge_nhoods %>% 
  st_join(apartmentrentals) %>% 
  group_by(name) %>% 
  summarize(count=n()) %>% 
  ungroup()
```
### Apartment rentals per Cambridge neighborhood 

## Map 1: Chloropleth

```{r}
cambridge_nhoods <- cambridge_nhoods %>%
  mutate(homesforrent = c(58, 88, 41, 120, 213, 102, 74, 
                       128, 162, 7, 139, 129, 148))

cambridge_nhoods$label <- 
  paste(cambridge_nhoods$name, "<br>", 
        cambridge_nhoods$homesforrent, "homes for rent") %>% 
  lapply(htmltools::HTML)

bins <- seq(min(cambridge_nhoods$homesforrent),
            max(cambridge_nhoods$homesforrent), by = 1)
pal <- colorNumeric("viridis", 
                    domain = cambridge_nhoods$homesforrent,
                    na.color = "#00000000")

leaflet(cambridge_nhoods) %>%
  addProviderTiles(providers$Stamen.TonerLite) %>%
  addPolygons(highlightOptions = highlightOptions(fillOpacity = 1),
              label = ~label,
              fillColor = ~pal(homesforrent),
              weight = 1, color = "black") %>% 
  addLegend(pal = pal, 
            values = ~homesforrent,
            bins = 3,
            opacity = 0.7, title = "Homes for rent",
            position = "topright")
```

## Map 2: Apartment rentals as points using centroids 

```{r}
MA_state_plane <- "+proj=lcc +lat_1=41.71666666666667 +lat_2=42.68333333333333 +lat_0=41 +lon_0=-71.5 +x_0=200000 +y_0=750000 +ellps=GRS80 +units=m +no_defs "

WGS84 <- "+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs"

nhood_points <- st_centroid(
  st_transform(cambridge_nhoods, crs = MA_state_plane)) %>%
  st_transform(WGS84)

leaflet(nhood_points) %>%
  addProviderTiles(providers$Stamen.TonerLite) %>%
  addCircles(label = ~label,
             fillColor = ~pal(homesforrent),
             stroke = FALSE, 
             radius = 50, 
             fillOpacity = 1) %>% 
  addLegend(pal = pal, 
            values = ~homesforrent,
            bins = 3,
            opacity = 0.7, title = "Homes for rent",
            position = "topright")
```


## Map 3: Continous Surface

```{r}
nhood_pts_sp <- nhood_points %>%
  st_transform(MA_state_plane) %>%
  as_Spatial()

nhood_poly_sp <- cambridge_nhoods %>%
  st_transform(MA_state_plane) %>%
  as_Spatial()
```
```{r}
cambridge_raster <- raster(nhood_poly_sp, res=10)
```

```{r}
gs <- gstat(formula=homesforrent~1, locations=nhood_pts_sp)
idw_interp <- interpolate(cambridge_raster, gs)

idw_interp_clip <- mask(idw_interp, nhood_poly_sp)
```

```{r}
leaflet(nhood_points) %>%
  addProviderTiles(providers$Stamen.TonerLite) %>%
  addRasterImage(idw_interp_clip, colors = pal, opacity = 0.8) %>% 
  addLegend(pal = pal, 
            values = ~homesforrent,
            bins = 3,
            opacity = 0.7, title = "Homes for rent",
            position = "topright")
```

## Discussions 

#### a.) Most Informative 

The most informative of the maps was map 3. The continuous surface feature allowed for a more spread out understanding of where homes for rent. Map 3 gave a more heat map based structure to the results. 

#### b-Most Interesting

The most interesting visually to me was map. The ability to interact with the map and view colorized changes I found visually interesting and exciting.

#### c-Most Appropriate to the Data 

Map 3 I feel was the most appropriate viewing of the data in that it provided a less spatially concrete understanding of where homes for rent were. Map 3 is more accurate and less misleading because even if there are 213 homes for rent, for example in the Cambridgeport area, these all may be situated in one particular corner of the boundary area or very diffusely located so the hotspot formation provides a more accurate viewing of the phenomena. 

#### d-Best

Map 3 was, to my mind, the best of the 3 maps I created in that it accurately understood the spatial relationship of the homes for rent across the boundaried area. 
